---
title: "**ShinyPET**: A Predictive, Exploratory and Text RShiny Application using Airbnb data"
poster_width: "23.39in"
poster_height: "33.11in"
font_family: 'Rasa'
title_text_fontfamily: 'Rasa'
author:
  - name: Ang Su Yiin
  - name: Joey Chua
  - name: Kevin Gunawan Albindo
  - name: Dr. Kam Tin Seong
    affil: 1
affiliation:
  - num: 1
    address: School of Computing and Information Systems, Singapore Management University
column_numbers: 3
# colour
primary_colour: '#FF5A60'
secondary_colour: '#FF5A60'
accent_colour: '#00A699'
# title body
logoleft_name: images/SMU_logo.jpg
logoright_name: images/airbnb.jpg
titlebox_bordercol:	"#0b4545"	#Colour of the title box border.
titlebox_borderwidth:	"0cm"	#Width of the title box border.
title_textcol: "#ffffff"
title_textsize: "60pt"
author_textcol: "#ffffff" 
author_textsize: '35pt'
affiliation_textsize: '25pt'
# poster body
body_textsize: "30px"
body_textcol: "#000000" #colour
column_margins: "0.5in"
columnline_col:	"#008080"	#Colour of the column line dividers.
columnline_width:	"1mm"	#Width of line between each column.
columnline_style:	dashed	#Style of the column line seperator.
sectitle_textcol:	"#ffffff"	#Colour of the poster section titles.
sectitle_textsize:	"40t"	#Text size of the section titles (H1).
sectitle2_textsize:	"30pt"	#Text size of the section titles (H2).
sectitle_bgcol:	"#00A699"	#Colour of the section title box.
sectitle_bordercol:	"#00A699"	#Colour of the border around the section title box.
sectitle_borderwidth:	"2mm"	#Thicknes of the section title box border.
sectitle_boxshape:	"4mm 0mm"	#Changes the shape of the section title box.
sectitle2_textcol:	"#00A699"	#Color of 2nd level header text.
link_col:	"#00A699"	#Colour of other links within the poster.
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

With the explosion of affordable data storage and processing technologies, the **demand for data-driven decision-making** (DDDM) has increased significantly. Research has shown that the use of data driven decision making through analytics tools had a positive impact on firm performance. Although there is an extensive range of commercial statistical tools, they are often **subscription-based** and **demand good technical knowledge** to mine and draw insights from. Therefore, it may not appeal to the average user. 

# Motivation

This project was motivated by the **increasing demand for data analytics** coupled with the **lack of open source tools** for users to perform analytics to undercover meaningful patterns from structured, textual and spatial data.

Using a collection of selected R packages, we have developed a R-Shiny application for the average user to perform exploratory and confirmatory analysis, text mining and predictive analysis to formulate insights and make data based decisions. With our application, we **aim to encourage anyone and everyone to make data-based decisions effortlessly**.

# Approach

A description of the techniques or algorithms you used to solve the problem.

3 modules
list of packages
design approach
wrangling -> output approach

# Exploratory 

asy include 3 modules write up

# Text

# Predictive



examples to be removed
```{r mytable, out.width='80%'}
knitr::kable(iris[1:10, 1:4], caption = 'Table caption.',align = 'c',"html")
```

Or with figures: Figure \@ref(fig:standard-plot), or Figure \@ref(fig:morefigs).

```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=5}
plot(mtcars[1:2])
```

```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}
data <- iris

plot(x = data$Sepal.Length, 
     y = data$Sepal.Width, 
     col = data$Species,
     pch = 19, 
     xlab = "Sepal Length (cm)",
     ylab = "Sepal Width (cm)")

```

# Further work

- Include a data load and wrangling function to accommodate different datasets.
- Combine text and explore module with coordinated linked views for multi-dimensional exploration.
- Predictive models currently limited to 5 models, additional models such as neural network can be included to provide user with wider model selection  


```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

